\documentclass[a4paper]{article}
\usepackage{array}
\usepackage{fontspec}
\setmainfont[Path=/usr/share/fonts/TTF/,
    BoldItalicFont=calibriz.ttf,
    BoldFont      =calibrib.ttf,
    ItalicFont    =calibrii.ttf]{calibri.ttf}

\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}

\newcommand{\myline}{\par
  \kern2pt % space above the rules
  \hrule height 0.5pt
  \kern2pt % space below the rules
}
\newcommand{\mybullet}{
	\indent \textbullet \hspace*{2mm}
}


\pagenumbering{gobble}

\begin{document}
	\begin{center}
		{\Large \textbf{Nischal Mahaveer Chand}} \\
		1179 Boylston Street, Apt. 38 | Fenway, Boston, MA 02215 \\% maybe put \\ ?
		(857) 277-9145 | mahaveerchand.n@husky.neu.edu \\
		%Available: Fall 2018 \\
	\end{center}
	
	\noindent
	{\large \textbf{TECHNICAL KNOWLEDGE}}
	\myline 
	
	\noindent
	\begin{tabular}{ m{3.5cm} l }
		\textbf{Languages: } & Python,\ C/C++,\ R,\ Java,\ SQL,\ JavaScript \\ % maybe include? HTML, Processing, JS, CSS, XML, JSON, Bash, Scala
		\textbf{Markup Languages: } & LaTeX,\ RMarkdown,\ Markdown,\ HTML,\ XML,\ JSON \\
		\textbf{Source Control: } & Git \\
		\textbf{Databases: } & MySQL, SQLite\\
		\textbf{Frameworks/Libraries: } & TensorFlow,\ pandas,\ scikit-learn,\ matplotlib,\ dplyr,\ ggplot2 \\
		\textbf{IDEs: } & RStudio,\ Jupyter Notebook,\ IntelliJ IDEA,\ PyCharm\\
		\textbf{Operating Systems: } & Linux,\ Windows,\ macOS \\
		\textbf{Office packages: } & Word,\ PowerPoint,\ Excel \\
		\textbf{Certifications: } & Introduction to Data Science in Python,\ R Programming,\ Introduction to Big Data 
	\end{tabular} \\

	\smallskip
	\noindent
	{\large \textbf{SKILLS}}
	\myline 
	\smallskip
	
	\mybullet Leader with strong technical background, and excellent analytical and problem-solving skills. \\
	\mybullet Decision-making ability, good communication, organizational, and interpersonal skills and goal oriented. \\
	\mybullet Ability to meet deadlines and handle pressure in coordinating multiple tasks in a work/project environment. \\
	
	\smallskip
	\noindent
	{\large \textbf{WORK EXPERIENCE}}
	\myline 
	\smallskip
	
	\noindent
	\textbf{untrodden labs}, Delhi, India \hfill Aug. 2016 \\
	\textit{Junior Intern}\\
	\mybullet Developed chatbot API for home automation system using NLKP. \\
	\mybullet Tested and debugged speech recognition module in Python. \\
	\mybullet Supervised test case runs for speech synthesis module in Python using TensorFlow. \\
	
	\noindent
	\textbf{MoodSense}, Bengaluru, India \hfill July-Oct. 2015 \\
	\textit{Senior Android Developer/Intern} \\
	\mybullet Designed and developed an android application in Android Studio using Java, XML, and SQLite. \\
	\mybullet Supervised team of 4. \\
	\mybullet The application improved user retention by 30\% for the startup. \\
	
	\noindent
	{\large \textbf{PERSONAL PROJECTS}}
	\myline 
	\smallskip
	
	\noindent
	\textbf{Ames Housing Price Prediction} \hfill Oct.-Dec. 2016 \\
	\mybullet Designed, developed, and tested advanced regression models in Python using the scikit-learn package in a team of 2. \\
	\mybullet Final model ranked under 1k on Kaggle. \\
	
	\noindent
	\textbf{Melody} - Open-Sourced Music Player Framework for Android \hfill July-Aug. 2015 \\
	\mybullet Designed and developed music player framework for Android using RxJava and Scala Reactive Extensions, which is 
			freely \indent\indent available under the MIT license and is commonly used by Android developers worldwide. \\
		
	\noindent
	{\large \textbf{EDUCATION}}
	\myline 
	\smallskip
	
	\noindent
	\textbf{NORTHEASTERN UNIVERSITY}, Boston, MA \\
	\indent College of Computer and Information Science \hfill Sept. 2017-present \\
	\indent \textit{Candidate for Master of Science in Data Science} \hfill Expected graduation: June 2019 \\
	\indent Related Courses: Algorithms, Introduction to Data Management and Processing \\
	
	\noindent
	\textbf{ALLIANCE UNIVERSITY}, Bengaluru, India \\
	\indent College of Engineering and Design, CGPA: 3.4/4.0 \hfill June 2017 \\
	\indent \textit{Bachelor of Technology in Computer Science Engineering} \\
	\indent Related Courses: Design and Analysis of Algorithms, Data Structures and Algorithms, Java Programming \\
	\indent Activities: Coordinator of CodeWars, Co-founder of DevMetric, Member of Linux Club \\
	\indent Honors and awards: Awarded financial aid for holding top rank in university\\
	
%	\noindent
%	{\large \textbf{INTERESTS/ACTIVITIES}}
%	\myline 
%	\smallskip
%		
%	\mybullet Competitive coding \\
%	\mybullet Swimming \\
%	\mybullet Stackoverflow \\
%	\mybullet CodeJam \\
%	\mybullet DevHack \\	
%	\mybullet CodeWars \\
%	\mybullet stuff i did
	
\end{document}