\documentclass[a4paper]{article}
\usepackage{array}
\usepackage{fontspec}
\setmainfont[Path=/usr/share/fonts/TTF/,
    BoldItalicFont=calibriz.ttf,
    BoldFont      =calibrib.ttf,
    ItalicFont    =calibrii.ttf]{calibri.ttf}

\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\newcommand{\myline}{\par
  \kern2pt % space above the rules
  \hrule height 0.5pt
  \kern2pt % space below the rules
}
\newcommand{\mybullet}{
	\indent \textbullet \hspace*{2mm}
}
\newcommand{\linetab}{
  \\ \hspace*{9mm}
}

\pagenumbering{gobble}

\begin{document}
	\begin{center}
		{\Large \textbf{Nischal Mahaveer Chand}} \\
    Boston, MA | \href{mailto:nischal.bhatewara@gmail.com}{nischal.bhatewara@gmail.com} | 
    (857) 277-9145 \\
                GitHub: \href{https://github.com/DarkestFloyd}{DarkestFloyd} | 
                LinkedIn: \href{https://www.linkedin.com/in/nischalmc}{nischalmc} |
		Medium: \href{https://medium.com/@darkestfloyd}{@darkestfloyd} \\
		Available: October 2019 \\
	\end{center}
	
	\noindent
	{\large \textbf{EDUCATION}}
	\myline 
	\smallskip
	
	\noindent
	\textbf{NORTHEASTERN UNIVERSITY}, Boston, MA \\
	Khoury College of Computer Sciences, GPA: 3.79/4.0 
        \hfill Sept 2017 - Aug 2019 \\
	\textit{Master of Science in Data Science} \\
        Related Courses: Supervised Machine Learning; 
        Unsupervised Machine Learning and Data Mining; \\
        \hspace*{23.9mm} Information Visualization;
        Natural Language Processing;
        Statistics for Bioinformatics; Algorithms \\
  % Teaching assistant positions: DS5110 (Spring 2019) and CS6220 (Summer 2019) \\
  Activities: - Founding member of the Khoury Data Science Hub - Data science community at Khoury College;\\
  \hspace*{14mm} - Selected speaker for GradTech Day (Tech talk on my work with Alzheimer's research at the Marcus Institute); \\
              \hspace*{14mm} - Presenter for NUVis (Presented MURA classification visualization to visualization experts at NEU);\\

 	\noindent
	\textbf{ALLIANCE UNIVERSITY}, Bengaluru, India \\
  College of Engineering and Design, CGPA: 3.4/4.0 \hfill Aug 2013 - June 2017 \\
	\textit{Bachelor of Technology in Computer Science Engineering} \\
  Related Courses: Data Mining and Data Warehousing; Big Data Analytics; Design and Analysis of Algorithms \\
	Activities: Coordinator of CodeWars; Member of DevMetric; Member of Linux Club \\
	
	\noindent
	{\large \textbf{TECHNICAL KNOWLEDGE}}
	\myline 
	
	\noindent
	\begin{tabular}{ m{2.5cm} l }
    \textbf{Languages: } & R (proficient), Python (proficient), SQL (intermediate), HTML/JavaScript (intermediate), Java (experienced) \\ 
    \textbf{Python Related: } & numpy, pandas, matplotlib, sklearn, scipy, TensorFlow, XGBoost, PyTorch, Keras, NLTK \\ 
    \textbf{R Related: } & tidyverse, caret, shiny, kableExtra, r2d3, RMarkdown \\
		\textbf{Tools and IDEs: } & git, Docker, flask, Weka Explorer, RStudio, 
                Jupyter Lab, IPython Notebook, Tableau \\
		% \textbf{Markup Languages: } & LaTeX, RMarkdown, Markdown, HTML, XML \\
	\end{tabular} \\

	\smallskip
	\smallskip
	\noindent
	{\large \textbf{WORK EXPERIENCE}}
	\myline 
	\smallskip
	
  \noindent
  \textbf{Khoury College of Computer Sciences}, Northeastern University, Boston, MA
  \hfill Jan 2019 - Aug 2019 \\
  \textit{Graduate Teaching Assistant}  \\
  \mybullet DS5110 - Introduction to Data Management and Processing (Spring 2019) \\
  \mybullet CS6220 - Unsupervised Machine Learing and Data Mining (Summer 2019) \\

  \noindent
  \textbf{\href{https://www.marcusinstituteforaging.org/}{Marcus Institute for Aging Research}}, 
  Hebrew SeniorLife, Roslindale, MA 
  \hfill July 2018 - Dec 2018 \\
        \textit{Co-op Student/Junior Data Scientist} \\
        \mybullet \textit{AD Supplement}: Performed regression analysis on high-dimensional
        clinical trials data in R to obtain valuable insights that \\ 
        \hspace*{9mm} directly affected active Alzheimer's research
        goals. Actively communicated results to senior researchers and the director. \\
        \mybullet \textit{Smartphone Lab project}: Built and migrated data gathering and 
        processing pipeline to fetch, process, and store inertial \\ 
        \hspace*{9mm} 
        motion sensor data onto local MySQL server in R, improving data gathering speeds 
        by 13\% and cutting licensing costs. \\ 
        \mybullet \textit{shinyMRI}: Built R ``Shiny'' powered application and module to 
        visualize 3D and 4D MRI images within a web-browser, \\
        \hspace*{9mm} improving diagnosis speeds for in-house 
        Alzheimer's research. Application received honorable mention by RStudio, Inc.\\
        
	% \noindent
	% \textbf{untrodden labs}, Delhi, India \hfill Aug. 2016 \\
        % \textit{R\&D Intern}\\
        % \mybullet Developed chatbot in Python using NLTK, for basic user interaction like 
        % weather reporting and reading daily news. \\
        % \mybullet Tested and debugged speech recognition modules using Google Speech 
        % Recognition API in Python. \\
	
	% \noindent
	% \textbf{MoodSense}, Bengaluru, India \hfill July - Oct. 2015 \\
	% \textit{Android Intern} \\
	% \mybullet Developed an android application that would recommend YouTube videos to a 
        % user based on his current mood \\
        % \hspace*{9mm} using Java, XML, and SQLite. The 
        % application improved user retention by 30\%. \\ 
	
\noindent
{\large \textbf{ACADEMIC PROJECTS}}
\myline 
\smallskip

      \noindent
      \textbf{\href{https://github.com/kuwisdelu/CardinalVis/}{CardinalVis}} - 
      Dashboard for dynamic visualization of Mass Spectrometry Imaging (MSI) experiments 
      \hfill May 2019 - current \\
      \mybullet Created and tested R ``Shiny'' modules to help non-technical researchers analyse 
      and visualize MSI experiments in R. \\
      \mybullet Application cuts down on research time by supporting fast and iterative exploration
      of MSI experiments in a web browser. \\

      \noindent
      \textbf{\href{https://github.com/DarkestFloyd/DS5500Project}{MURA}} - Bone X-ray image 
      classification and visualization project \hfill Jan 2019 - Apr 2019 \\
      \mybullet Trained hierarchical CNN models to classify X-ray images as normal or abnormal 
      using PyTorch and torchvision in Python. \\
      \mybullet Created dynamic visualization of activation mapping over training iteration for 
      x-ray images using D3.js and Javascript. \\
      \mybullet Created RESTful API service to provide real-time classification and 
      activation maps using Flask-RESTful in Python. \\
      \mybullet Deployed application, models, and visualization to Amazon EC2 instance. \\

			\noindent
      \textbf{\href{https://github.com/DarkestFloyd/NL2code}{NL2code}} - Natural Language to 
      Python code generator \hfill Jan 2018 - Apr 2018 \\
      \mybullet Scraped open-source Python repositories to gather training data of 
      code-comment pairs using beautifulsoup in Python. \\
      \mybullet Performed semantic analysis and canonicalization of raw data using NLTK and Python. \\
      \mybullet Trained and tested neural machine translation models using TensorFlow in Python and in Theano. \\
      \mybullet Improved BLUE score over base paper by augmenting semantic information to feature embedding. \\

			\noindent
      \textbf{\href{https://sichenghao1992.shinyapps.io/DS5110/}{Flashlight}} - Property 
			Assessment Visualization for the City of Boston \hfill Oct 2017 - Dec 2017 \\
      \mybullet Created dashboard to visualize various aspects of property assessment values 
      using R ``Shiny'' and Leaflet in R. \\
      \mybullet Geocoded missing coordinate values using Open Address dataset and Google Maps Geocode API in Python. \\
      \mybullet Created Python scripts to automate conversion of Zillow's shapefiles to GeoJSON format and gathering of meta-data. \\ 
			
			% \noindent
			% \textbf{Movie Recommendation System} \hfill Apr 2017 - June 2017\\
			% \mybullet Implemented a Recurrent Neural Network using TensorFlow in Python to recommend 
      % movies to a user. By analysing \\ \hspace*{9mm} the sequence of movies reviewed, we were 
      % able to achieve high scores in peer review. \\ 

	% \noindent
	% {\large \textbf{PERSONAL PROJECTS}}
	% \myline 
	% \smallskip
	
		% \noindent
		% \textbf{Ames Housing Price Prediction} \hfill Oct. - Dec. 2016 \\
    % \mybullet Created regression models in Scikit-Learn and neural models in TensorFlow to 
    % predict housing prices in Python. \\
    % \mybullet Best submission one of top 20\% on Kaggle public leaderboard. \\
		
		% \noindent
		% \textbf{Melody} - Open-Sourced Music Player Framework for Android \hfill July - Aug. 2015\\
		% \mybullet Designed and developed music player framework for Android using RxJava and 
					% Scala Reactive Extensions, which is freely\\ \hspace*{9mm} available under the MIT 
          % license and is commonly used by Android developers worldwide. \\
	
	% \noindent
	% {\large \textbf{HONORS AND ACHIEVEMENTS}}
	% \myline 
	% \smallskip

    % \mybullet Presented \textit{MURA visualization tool} at The Northeastern University 
    % Visualization Consortium. \hfill Apr 2019 \\
    % \mybullet Honorable mention for \textit{shinyMRI} in RStudio's first Shiny contest. 
    % \hfill Apr 2019 \\
    % \mybullet Graduate speaker for TechTalks at Grad TechDay, Khoury College. \hfill Mar 2019 \\
	% 	\mybullet Coordinated and organized CodeWars, a 24-hour hackathon as part of 
	% 	university fest at Alliance University.\hfill Oct 2015\\
		% \mybullet Volunteer for planting 300 saplings as part of reforestation drive in 
		% Shivaganga Hills, India. \hfill Sept. 2014 \\
		% \mybullet Volunteer for collecting disaster relief supplies for the Uttarakhand Floods 
		% of 2013. \hfill Sept. 2013 \\
		% \mybullet Awarded Karnataka state scholarship, covering 70\% tuition fee for undergraduate 
		% study at Alliance University. \hfill 2013 - 2017 \\
		
\end{document}
