\documentclass[a4paper]{article}
\usepackage{array}
\usepackage{fontspec}
\setmainfont[Path=/usr/share/fonts/TTF/,
    BoldItalicFont=calibriz.ttf,
    BoldFont      =calibrib.ttf,
    ItalicFont    =calibrii.ttf]{calibri.ttf}

\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\newcommand{\myline}{\par
  \kern2pt % space above the rules
  \hrule height 0.5pt
  \kern2pt % space below the rules
}
\newcommand{\mybullet}{
	\indent 
  \textbullet \hspace*{2mm}
}
\newcommand{\mysubbullet}{
	\indent 
  - \hspace*{2mm}
}
\newcommand{\linetab}{
  \\ \hspace*{9mm}
}

\pagenumbering{gobble}

\begin{document}
	\begin{center}
		{\LARGE \textbf{Nischal Mahaveer Chand}} \\
    Boston, MA | 
    \href{mailto:nischal.bhatewara@gmail.com}{nischal.bhatewara@gmail.com} | 
    % (857) 277-9145 |  
    LinkedIn: \href{https://www.linkedin.com/in/nischalmc}{nischalmc} \\
		Blog: \href{https://medium.com/@darkestfloyd}{medium.com/@darkestfloyd} |
    Google Scholar: \href{https://scholar.google.com/citations?user=G8ALRj8AAAAJ}{Nischal Mahaveer Chand} |
                GitHub: \href{https://github.com/darkestfloyd}{DarkestFloyd} \\
		% Available: October 2019 \\
	\end{center}

  \smallskip
  \smallskip
	\noindent
	{\large \textbf{SUMMARY}}
	\myline 
	\smallskip

  \mybullet Senior Data Scientist with experince applying machine learning and deep learning techniques to biomedical and \\\hspace*{10mm}multi-omics data in durg discovery, theraputics, and diagnostics. \\
  \mybullet Skilled in data-wrangling, machine learning, and statistical analysis techniques to extract value from messy datasets. \\
  \mybullet Strong understanding of data visualization techniques and story telling to deliver key results to diverse audiences. \\
  \mybullet Experienced in communicating with executive team to understand business needs and commercialization objectives to \\\hspace*{10mm}provide analytics solutions that help drive business decisions. \\
  \mybullet Proficient in R, Python, SQL, Java, and linux based operating systems. \\ 
  \mybullet Committed to improving patient journeys and outcomes as they battle disease. \\

	\smallskip
	\smallskip
	\noindent
	{\large \textbf{WORK EXPERIENCE}}
	\myline 
	\smallskip
	
  \noindent
  \textbf{\href{https://www.bpgbio.com/}{BPGbio, Inc.}}, Framingham, MA \\
  Datasets: high-throughput multi-omics, NGS, drug sensitivity, EMR/EHR, molecular assay, public domain \\
  Tools: R, Python, R Shiny, tidyverse, git, linux, tensorflow, keras, pandas, ggplot2, caret, postman, Azure, Docker \\
  \textit{Senior Data Scientist} \hfill Jan 2023 - present \\
  \mybullet Researched and developed deep learning algorithms to provide computational support in compound discovery and \\\hspace*{10mm}indication selection pipelines by leveraging cell line omics and compound structural data in Python using Keras. \\
  \mybullet Developed machine learning and visualization pipeline to support commercialization objective of diagnostic test with an \\\hspace*{10mm}emphasis on model interpretability in R (caret) and Python (sklearn). \\
  \mybullet Created code book with best practices for utilizing machine learning in diagnostics for clinical use in MS Word. \\
  \mybullet Prepared and presented key results and progress updates at company wide scientific meetings using MS PowerPoint. \\
  \\
  \textit{Data Scientist I/II/III} \hfill Nov 2019 - Dec 2023 \\
  \mybullet Developed data pipelines to process and integrate large datasets from disparate sources to support company decision \\\hspace*{10mm}making and guide diagnostics and therapeutics strategies in R (tidyverse) and Python (Pandas). \\
  \mybullet Implemented and deployed deep learning solution to provide optimal parameters for running internal platform bAIcis to \\\hspace*{10mm}reduce operational costs and increase user productivity in Python using sklearn and Keras. \\
  \mybullet Deployed data pipelines, models, and dashboards on Azure using Docker to enable external collaborators to access and \hspace*{10mm}use the pipelines for data-driven decision making. \\
  % \mybullet Developed machine learning solutions using random forests, SVMs, penalized regressions, and deep neural networks in \\\hspace*{10mm}R and Python to facilitate data driven decisions in diagnostics and therapeutics development. \\
  % \mybullet Implemented standardized data pipelines to ingest and process data from external vendor APIs, MySQL databases, \\\hspace*{10mm}publicly available resources and webpages, and open databases using R, Python, cron, Linux. \\
  \mybullet Performed statistical data analysis on longitudinal multi-omics datasets to reveal biologically relevant insights in R \\\hspace*{10mm}using tidyverse resulting in development of validation molecular assays, project funding, and publications. \\
  \mybullet Scaled legacy data pipelines by identifying and incorporating multi-processing techniques to improve data processing \hspace*{10mm}speeds by upto 70\% in R using parallel. \\
  \mybullet Collaborated with internal R\&D team to guide experimental design and provide statistical and computational support. \\
  \mybullet Developed and deployed dashboards to provide automation capabilities for routine tasks for R\&D teams and provide \\\hspace*{10mm}overview of key metrics for program managers to help guide project decisions in R uning RShiny. \\
  \mybullet Communicated insights to diverse audiences including data scientists, clinicians, senior leadership teams, scientific teams, \\\hspace*{10mm}and external collaborators via presentations and reports using MS PowerPoint and MS Word. \\
  % \mybullet Identified automation opportunities to implement R Shiny dashboards. \\
  \mybullet Developed, documented, and maintained internal packages and linux shell scripts to fill Analytics team needs. \\
  % \mybullet Supported internal scientific and omics teams by understanding requirements and conducting data experiments. \\
  % \mybullet Collaborated with external software engineering and data science teams as well as interacted with external cloud and \\\hspace*{10mm}technology vendors to communicate requirements. \\ 
  \\
  \textit{Interim Linux System Administrator} \hfill Mar 2021-Nov 2022 \\ Tools: ganglia, cron, ssh, linux, mpi, slurm, fstab  \\
  \mybullet Provided support to analytics team by managing software stack of internal production servers and onsite HPC cluster. \\
  \mybullet Deployed internal bAIcis platform on Azure resulting in increased scale while staying compliant, enabling team to execute \hspace*{10mm}on more than one projects. \\

  \noindent
  \textbf{\href{https://www.marcusinstituteforaging.org/}{Marcus Institute for Aging Research}}, 
  Hebrew SeniorLife, Roslindale, MA \\
        \textit{Junior Data Scientist / Co-op Student} \hfill July 2018 - Dec 2018 \\
        Datasets: patient forms and cognitive test scores, MRI and fMRI, radiologist annotations, accelerometer senor time-series \\
        Tools: R, SQL, tidyverse, git \\
        \mybullet \textit{AD Supplement}: 
        \hspace*{3.7 mm} - Performed regression analysis and hypothesis testing
        on in-house patient data using R and SQL. \\
        % \hspace*{37.5 mm} - Directly impacted active Alzheimer's research goals. \\
        \hspace*{37.5 mm} - Prepared reports and actively communicated results to researchers and institute director.  \\
        \mybullet \textit{Smartphone Lab}: 
        \hspace* {2.3 mm} - Built data processing pipelines to clean and process time-series sensor data from wearable tracking \hspace*{40mm}device using R and SQL. \\
        \mybullet \textit{shinyMRI}: 
        \hspace* {12.7 mm} - Built R shiny application to visualize 3D and 4D MRI images. \\
        \hspace*{37.5 mm} - Improved diagnosis speed for in-house Alzheimer's research. \\
        \hspace*{37.5 mm} - Application received honorable mention by RStudio, Inc. \\
        
	% \noindent
	% \textbf{untrodden labs}, Delhi, India \hfill Aug 2016 \\
        % \textit{Chatbot R\&D Intern}\\
        % \mybullet Developed chatbots in Python using NLTK for user interaction like 
        % weather reporting and reading daily news. \\
        % \mybullet Tested and debugged speech recognition modules using Google Speech 
        % Recognition API in Python. \\
	
	% \noindent
	% \textbf{MoodSense}, Bengaluru, India \hfill July - Oct 2015 \\
	% \textit{Android Intern} \\
  % \mybullet Built and tested android application for an entertainment startup using Java, XML, 
        % and SQLite with complex user interactions. \\
  % \mybullet Implemented custom UI elements to enable drag-to-minimize feature similar to YouTube.\\
  % \mybullet Worked with OAuth for user authentication and getting user data from Google. \\
  % \mybullet 
	% \mybullet Developed android application that would recommend YouTube videos to a 
        % user based on his current mood \\
        % \hspace*{9mm} using Java, XML, and SQLite. The 
        % application improved user retention by 30\%. \\ 


  \newpage
	\noindent
	{\large \textbf{PUBLICATIONS}}
	\myline 
	\smallskip

  \mybullet (Co-author) Miller, G.M., et al. Hypothesis-Agnostic Network-Based Analysis of Real-World Data Suggests Ondansetron \hspace*{10mm}is Associated with Lower COVID-19 Any Cause Mortality. Drugs - Real World Outcomes 9, 359–375 (2022). \\
  \mybullet (Co-author) Kiebish, M.A., Tekumalla, P., Ravipaty, S. et al. Clinical utility of a serum biomarker panel in distinguishing \hspace*{10mm}prostate cancer from benign prostate hyperplasia. Sci Rep 11, 15052 (2021). \\
  \mybullet (Co-author) Grund, Eric M., et al. "Project Survival®: Discovery of a molecular-clinical phenome biomarker panel to \hspace*{10mm}detect pancreatic ductal adenocarcinoma among at risk populations using high-fidelity longitudinal phenotypic and \hspace*{10mm}multi-omic analysis." Cancer Research 82.12\_Supplement (2022): 5145-5145. \\
  \mybullet (Co-author) Moser, A. J., et al. "1485P Identification of novel protein biomarkers for FOLFIRINOX-based chemotherapy \hspace*{10mm}response in advanced pancreatic adenocarcinoma using patient omics and Bayesian AI." Annals of Oncology 32 (2021).\\ %: \hspace*{10mm}S1094.\\
  \mybullet (Co-author) Moser, A. J., et al. "1547P Project Survival®: High-fidelity longitudinal phenotypic and multi-omic \\\hspace*{10mm}characterization of pancreatic ductal adenocarcinoma (PDAC) for biomarker discovery." Annals of Oncology 31 (2020).\\%: \\\hspace*{10mm}S947-S948.\\
	

	\noindent
	{\large \textbf{EDUCATION}}
	\myline 
	\smallskip
	
	\noindent
	\textbf{NORTHEASTERN UNIVERSITY}, Boston, MA \\
	Khoury College of Computer Sciences, GPA: 3.79/4.0 
        \hfill Sept 2017 - Aug 2019 \\
	\textit{Master of Science in Data Science} \\
        Related Courses: Supervised Machine Learning; 
        Unsupervised Machine Learning and Data Mining; \\
        \hspace*{23.9mm} Data Visualization;
        Natural Language Processing;
        Statistics for Bioinformatics; Algorithms \\
  Achievements: - Judge and panelist for Northeastern University UNCOVER COVID datathon (Sep 2020) \\
  \hspace*{21.2mm} - Presenter at Northeastern University Visualization Consortium (April 2019)\\ %- Presented MURA data visualization to visualization experts;\\
  \hspace*{21.2mm} - Selected speaker for Northeastern University GradTech Day tech talk (March 2019) \\%- Presented tech talk on my work in Alzheimer's research at the Marcus Institute; \\
  TA positions: Data Management in R (Spring 2019); Unsupervised Machine Learning (Summer 2019) \\

 	\noindent
	\textbf{ALLIANCE UNIVERSITY}, Bengaluru, India \\
  College of Engineering and Design, CGPA: 3.4/4.0 \hfill Aug 2013 - June 2017 \\
	\textit{Bachelor of Technology in Computer Science and Engineering} \\
  Related Courses: Data Mining and Data Warehousing; Big Data Analytics; Design and Analysis of Algorithms \\

% \newpage
% \noindent
% {\large \textbf{TECHNICAL KNOWLEDGE}}
% \myline 
	
% 	\noindent
% 	\begin{tabular}{m{2.5cm} l }
%     % \textbf{Languages: } & R (proficient), Python (proficient), SQL (intermediate), HTML/JavaScript (intermediate), Java (experienced) \\ 
%     \textbf{Python Packages: } & NumPy, Pandas, Matplotlib, Scikit-learn, SciPy, TensorFlow, XGBoost, PyTorch, Keras \\ 
%     \textbf{R Packages: } & dplyr, ggplot2, leaflet, caret, tidyverse, shiny, kableExtra, RMarkdown \\
%     \textbf{Other Tools: } & git, Docker, flask, MySQL, Jupyter Notebook, AWS \\
% 		% \textbf{Markup Languages: } & LaTeX, RMarkdown, Markdown, HTML, XML \\
% 	\end{tabular} \\ \\
	
\noindent
{\large \textbf{RELEVANT ACADEMIC PROJECTS}}
\myline 
\smallskip

      \noindent
      \textbf{CardinalVis} - 
      Dynamic data visualization for Mass Spectrometry Imaging (MSI) experiments 
      \hfill May 2019 - Aug 2019 \\
      \hfill \textit{Project Report: \href{https://github.com/darkestfloyd/CardinalVis\_AppNote/blob/master/Summer\%20Full\%20Project\%20Final\%20Report.pdf}{https://github.com/darkestfloyd/CardinalVis\_AppNote}}\\
      % \hfill \textit{Project Repository: \href{https://github.com/kuwisdelu/CardinalVis/}{https://github.com/kuwisdelu/CardinalVis/}}\\
      \mybullet Created R shiny dashboard and modules in R to visualize mass-spectrometry data. \\
      \mybullet Application is open-sourced and intended to cut down research times in MSI experiment research. \\

      \noindent
      \textbf{\href{https://github.com/darkestfloyd/DS5500Project}{MURA}} - Bone X-ray image 
      classification and data visualization project \hfill Jan 2019 - Apr 2019 \\
      % \hfill \textit{Website: \href{http://ec2-3-212-216-62.compute-1.amazonaws.com/}{http://ec2-3-212-216-62.compute-1.amazonaws.com/}}\\
      Summary: End of course project to improve interpretability in black box ML models; worked in a team of 4. \\
      \hfill Project Repository: \href{https://github.com/darkestfloyd/DS5500Project}{https://github.com/darkestfloyd/DS5500Project}\\
      Tools: Python, PyTorch, torchvision, scikit-learn, AWS \\
      % \mybullet Trained and tuned CNN classification models using PyTorch and torchvision in Python. \\
      \mybullet Implemented image processing pipeline for adding image rotation, scaling, etc to enlarge training set using torchvision. \\
      % \mybullet Trained and tuned machine learning classification models to establish baseline models in sklearn. \\
      \mybullet Trained and tuned deep learning classification models for prediction of bone condition using PyTorch. \\
      \mybullet Integrated GradCAM technique to visualize localization map of gradients for model interpretation in PyTorch. \\
      % \mybullet Obtained best models for each classified using Cohen's Kappa metric. \\
      % \mybullet Created dynamic data visualization to explore models and confusion matrix 
        % using D3.js and Javascript. \\
      % \mybullet Created RESTful API service to provide real-time classification and dynamic visualizations
      % using Flask-RESTful in Python. \\
      \mybullet Depluyed model and provide real-time prediction for user uploaded image on AWS. \\
      % \mybullet Future Work: Implement online learning technique to incorporate feedback from
      % UI to backend model. \\

			\noindent
      \textbf{\href{https://github.com/darkestfloyd/NL2code}{NL2code}} - Natural Language to 
      Python code generator \hfill Jan 2018 - Apr 2018 \\
      Summary: End of course project to implement NLP techniques; worked in a team of 3. \\
      \hfill Project Repository: \href{https://github.com/darkestfloyd/NL2code}{https://github.com/darkestfloyd/NL2code}\\
      Tools: Python, TensorFlow, Theano, beautifulsoup, NLTK, git \\
      \mybullet Implemented data ingestion pipeline to scrape Python code and associated comments from public GitHub repositories 
      \hspace*{10mm}to gather training data in Python using beautifulsoup. \\
      % \mybullet Scraped open-source Python repositories to gather training data using beautifulsoup in Python. \\
      % \mybullet Performed data manipulation using NLTK and Python. \\
      \mybullet Trained encoder-decoder models in Theano to convert english comments (natural language) to Python code. \\
      \mybullet Improved accuracy and BLUE score over base paper by incorporating grammatical strucutre into encoder. \\
      % \mybullet Significant accuracy improvement and minor BLUE score improvement over base paper. \\
      % \mybullet Future Work: Scrape data from leading machine learning repositories in Python for better generalization. \\

% 			\noindent
%       \textbf{\href{https://sichenghao1992.shinyapps.io/DS5110/}{Flashlight}} - Real Estate 
%       Property Assessment Visualization for the City of Boston \hfill Oct 2017 - Dec 2017 \\
%       \mybullet Created dashboard to visualize various aspects of real estate assessment values 
%       using R ``Shiny'' and Leaflet in R. \\
%       \mybullet Geocoded missing coordinate values using Open Address dataset and Google Maps Geocode API in Python. \\
%       \mybullet Created Python scripts to automate conversion of Zillow's shapefiles to GeoJSON format and gathering of meta-data. \\ 
			
% 			\noindent
% 			\textbf{Movie Recommendation System} \hfill Apr 2017 - June 2017\\
% 			\mybullet Implemented a Recurrent Neural Network using TensorFlow in Python to recommend 
%       movies to a user. By analysing \\ \hspace*{9mm} the sequence of movies reviewed, we were 
%       able to achieve high scores in peer review. \\ 

% 	% \noindent
% 	% {\large \textbf{PERSONAL PROJECTS}}
% 	% \myline 
% 	% \smallskip
	
% 		% \noindent
% 		% \textbf{Ames Housing Price Prediction} \hfill Oct. - Dec. 2016 \\
%     % \mybullet Created regression models in Scikit-Learn and neural models in TensorFlow to 
%     % predict housing prices in Python. \\
%     % \mybullet Best submission one of top 20\% on Kaggle public leaderboard. \\
		
% 		% \noindent
% 		% \textbf{Melody} - Open-Sourced Music Player Framework for Android \hfill July - Aug. 2015\\
% 		% \mybullet Designed and developed music player framework for Android using RxJava and 
% 			% 		Scala Reactive Extensions, which is freely\\ \hspace*{9mm} available under the MIT 
          % license and is commonly used by Android developers worldwide. \\
	
	% \noindent
	% {\large \textbf{HONORS AND ACHIEVEMENTS}}
	% \myline 
	% \smallskip

    % \mybullet Panelist for Northeastern University UNCOVER COVID datathon. \hfill Sep 2020 \\
    % \mybullet Presented \textit{MURA visualization tool} at The Northeastern University 
    % Visualization Consortium. \hfill Apr 2019 \\
    % \mybullet Honorable mention for \textit{shinyMRI} by RStudio. \hfill Apr 2019 \\
    % \mybullet Graduate speaker for TechTalks at Grad TechDay, Khoury College. \hfill Mar 2019 \\
	% 	\mybullet Coordinated and organized CodeWars, a 24-hour hackathon as part of 
	% 	university fest at Alliance University.\hfill Oct 2015\\
		% \mybullet Volunteer for planting 300 saplings as part of reforestation drive in 
		% Shivaganga Hills, India. \hfill Sept. 2014 \\
		% \mybullet Volunteer for collecting disaster relief supplies for the Uttarakhand Floods 
		% of 2013. \hfill Sept. 2013 \\
		% \mybullet Awarded Karnataka state scholarship, covering 70\% tuition fee for undergraduate 
		% study at Alliance University. \hfill 2013 - 2017 \\


\end{document}
