\documentclass[a4paper]{article}
\usepackage{array}
\usepackage{fontspec}
\setmainfont[Path=/usr/share/fonts/TTF/,
    BoldItalicFont=calibriz.ttf,
    BoldFont      =calibrib.ttf,
    ItalicFont    =calibrii.ttf]{calibri.ttf}

\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\newcommand{\myline}{\par
  \kern2pt % space above the rules
  \hrule height 0.5pt
  \kern2pt % space below the rules
}
\newcommand{\mybullet}{
	\indent 
  \textbullet \hspace*{2mm}
}
\newcommand{\mysubbullet}{
	\indent 
  - \hspace*{2mm}
}
\newcommand{\linetab}{
  \\ \hspace*{9mm}
}

\pagenumbering{gobble}

\begin{document}
	\begin{center}
		{\LARGE \textbf{Nischal Mahaveer Chand}} \\
    Boston, MA | 
    \href{mailto:nischal.bhatewara@gmail.com}{nischal.bhatewara@gmail.com} | 
    (857) 277-9145 \\
		Blog: \href{https://medium.com/@darkestfloyd}{medium.com/@darkestfloyd} |
    LinkedIn: \href{https://www.linkedin.com/in/nischalmc}{nischalmc} |
                GitHub: \href{https://github.com/darkestfloyd}{DarkestFloyd} \\
		% Available: October 2019 \\
	\end{center}
	
	% \noindent
	% {\large \textbf{SUMMARY}}
	% \myline 
	% \smallskip

  % Data science graduate from top-tier university with hands-on experience 
  % extracting insights from large clinical trials datasets in a healthcare research setting.
  % In depth knowledge of machine learning and deep-learning algorithms rooted in mathematics.
  % Able to collaborate with research teams to understand requirements and produce
  % analytical and software solutions.
  % Demonstrated ability to communicate results to non-technical audiences. 
  % Innately curious individual, passionate to further healthcare research. \\

	\smallskip
	\smallskip
	\noindent
	{\large \textbf{WORK EXPERIENCE}}
	\myline 
	\smallskip
	
  \noindent
  \textbf{\href{https://www.berghealth.com/}{BERG LLC}}, Framingham, MA \\
  \textit{Data Scientist III} \hfill Nov 2019 - present \\
  Datasets: longitudinal high-throughput multi-omics, NGS, post translational modifications, EHR, molecular assay \\
  Tools: R, RStudio, R Shiny, tidyverse, git, linux, xgboost, glm, ggplot2, caret, Keras, postman, Azure \\
  \mybullet Implemented standardized data pipelines to ingest and process data from external vendor APIs, MySQL databases, 
  \\\hspace*{10mm}publicly available resources and webpages, and open databases using R, Python, cron, Linux. \\
  \mybullet Performed statistical data analysis in R on biological datasets to reveal actionable insights into disease models resulting \\\hspace*{10mm}in development of molecular assays, project funding, publications, and conference posters.\\
  \mybullet Developed machine learning solutions using random forests, SVMs, penalized regressions, and deep neural networks in \\\hspace*{10mm}R and Python to facilitate data driven decisions. \\
  \mybullet Developed dashboards and visualizations in R using RShiny and ggplot2 for internal use and publications. \\
  \mybullet Communicated insights to data scientists, clinicians, senior leadership, and scientific teams via presentations and reports. \\
  % \mybullet Identified automation opportunities to implement R Shiny dashboards. \\
  \mybullet Developed, documented, and maintained R packages and linux shell scripts to fill Analytics team needs. \\
  \mybullet Supported internal scientific and omics teams by understanding requirements and conducting data experiments. \\
  \mybullet Collaborated with external software engineering and data science teams as well as interacted with external cloud and \\\hspace*{10mm}technology vendors to communicate requirements. \\ \\ 
  \textit{Interim Linux System Administrator} \hfill Mar 2021-Mar 2022 \\ Tools: ganglia, cron, ssh, linux, mpi, slurm, fstab  \\
  \mybullet Provided support to analytics team by managing software stack of internal production servers and onsite HPC cluster. \\

  \noindent
  \textbf{\href{https://www.marcusinstituteforaging.org/}{Marcus Institute for Aging Research}}, 
  Hebrew SeniorLife, Roslindale, MA \\
        \textit{Junior Data Scientist / Co-op Student} \hfill July 2018 - Dec 2018 \\
        \mybullet \textit{AD Supplement}: 
        \hspace*{3.7 mm} - Performed regression analysis and hypothesis testing
        on clinical trials data using R and SQL. \\
        % \hspace*{37.5 mm} - Directly impacted active Alzheimer's research goals. \\
        \hspace*{37.5 mm} - Actively communicated results to directors and researchers.  \\
        \mybullet \textit{Smartphone Lab}: 
        \hspace* {2.3 mm} - Built data processing pipelines for time-series sensor data using R and SQL. \\
        \hspace*{37.5 mm} - Improved data processing speeds by upto 13\%. \\ 
        \mybullet \textit{shinyMRI}: 
        \hspace* {12.7 mm} - Built scalable R shiny application to visualize 3D and 4D MRI images. \\
        \hspace*{37.5 mm} - Improved diagnosis speed for in-house Alzheimer's research. \\
        \hspace*{37.5 mm} - Application received honorable mention by RStudio, Inc. \\
        
	% \noindent
	% \textbf{untrodden labs}, Delhi, India \hfill Aug 2016 \\
        % \textit{R\&D Intern}\\
        % \mybullet Developed chatbots in Python using NLTK for basic user interaction like 
        % weather reporting and reading daily news. \\
        % \mybullet Tested and debugged speech recognition modules using Google Speech 
        % Recognition API in Python. \\
	
	% \noindent
	% \textbf{MoodSense}, Bengaluru, India \hfill July - Oct 2015 \\
	% \textit{Android Intern} \\
  % \mybullet Built and tested android application for an entertainment startup using Java, XML, 
        % and SQLite with complex user interactions. \\
  % \mybullet Implemented custom UI elements to enable drag-to-minimize feature similar to YouTube.\\
  % \mybullet Worked with OAuth for user authentication and getting user data from Google. \\
  % \mybullet 
	% \mybullet Developed android application that would recommend YouTube videos to a 
        % user based on his current mood \\
        % \hspace*{9mm} using Java, XML, and SQLite. The 
        % application improved user retention by 30\%. \\ 

	\noindent
	{\large \textbf{EDUCATION}}
	\myline 
	\smallskip
	
	\noindent
	\textbf{NORTHEASTERN UNIVERSITY}, Boston, MA \\
	Khoury College of Computer Sciences, GPA: 3.79/4.0 
        \hfill Sept 2017 - Aug 2019 \\
	\textit{Master of Science in Data Science} \\
        Related Courses: Supervised Machine Learning; 
        Unsupervised Machine Learning and Data Mining; \\
        \hspace*{23.9mm} Data Visualization;
        Natural Language Processing;
        Statistics for Bioinformatics; Algorithms \\
  % Achievements: - Judge and panelist for Northeastern University UNCOVER COVID datathon (Sep 2020) \\
  % \hspace*{21.2mm} - Presenter at Northeastern University Visualization Consortium (April 2019)\\ %- Presented MURA data visualization to visualization experts;\\
  % \hspace*{21.2mm} - Selected speaker for Northeastern University GradTech Day tech talk (March 2019) \\%- Presented tech talk on my work in Alzheimer's research at the Marcus Institute; \\
  TA positions: Data Management in R (Spring 2019); Unsupervised Machine Learning (Summer 2019) \\

 	\noindent
	\textbf{ALLIANCE UNIVERSITY}, Bengaluru, India \\
  College of Engineering and Design, CGPA: 3.4/4.0 \hfill Aug 2013 - June 2017 \\
	\textit{Bachelor of Technology in Computer Science and Engineering} \\
  Related Courses: Data Mining and Data Warehousing; Big Data Analytics; Design and Analysis of Algorithms \\

	\noindent
	{\large \textbf{PUBLICATIONS}}
	\myline 
	\smallskip

  \mybullet (Co-author) Kiebish, M.A., Tekumalla, P. et al. Clinical utility of a serum biomarker panel in distinguishing 
  prostate \hspace*{10mm}cancer from benign prostate hyperplasia. Sci Rep 11, 15052 (2021). https://doi.org/10.1038/s41598-021-94438-4 \\
  \mybullet (Co-author) Miller, Gregory M., et al. "Ondansetron use is associated with lower COVID-19 mortality in a Real-World Data \hspace*{10mm}network-
  based analysis." medRxiv (2021). \\
  \mybullet (Co-author) Moser, A. J., et al. "1485P Identification of novel protein biomarkers for FOLFIRINOX-based chemotherapy \hspace*{10mm}response in advanced pancreatic adenocarcinoma using patient omics and Bayesian AI." Annals of Oncology 32 (2021): \hspace*{10mm}S1094.\\
  % \mybullet (Co-author) Moser, A. J., et al. "1547P Project Survival®: High-fidelity longitudinal phenotypic and multi-omic \\\hspace*{10mm}characterization of pancreatic ductal adenocarcinoma (PDAC) for biomarker discovery." Annals of Oncology 31 (2020): \\\hspace*{10mm}S947-S948.\\
	
\newpage
% \noindent
% {\large \textbf{TECHNICAL KNOWLEDGE}}
% \myline 
	
% 	\noindent
% 	\begin{tabular}{m{2.5cm} l }
%     % \textbf{Languages: } & R (proficient), Python (proficient), SQL (intermediate), HTML/JavaScript (intermediate), Java (experienced) \\ 
%     \textbf{Python Packages: } & NumPy, Pandas, Matplotlib, Scikit-learn, SciPy, TensorFlow, XGBoost, PyTorch, Keras \\ 
%     \textbf{R Packages: } & dplyr, ggplot2, leaflet, caret, tidyverse, shiny, kableExtra, RMarkdown \\
%     \textbf{Other Tools: } & git, Docker, flask, MySQL, Jupyter Notebook, AWS \\
% 		% \textbf{Markup Languages: } & LaTeX, RMarkdown, Markdown, HTML, XML \\
% 	\end{tabular} \\ \\
	
\noindent
{\large \textbf{RELEVANT PROJECTS}}
\myline 
\smallskip

      \noindent
      \textbf{\href{https://github.com/kuwisdelu/CardinalVis/}{CardinalVis}} - 
      Dynamic data visualization for Mass Spectrometry Imaging (MSI) experiments 
      \hfill May 2019 - Aug 2019 \\
      \hfill \textit{Project Repository: \href{https://github.com/kuwisdelu/CardinalVis/}{https://github.com/kuwisdelu/CardinalVis/}}\\
      \mybullet Created R shiny dashboard and modules in R. \\
      \mybullet Application is open-sourced and intended to cut down research times in MSI experiment research. \\

      \noindent
      \textbf{\href{http://ec2-3-212-216-62.compute-1.amazonaws.com/}{MURA}} - Bone X-ray image 
      classification and data visualization project \hfill Jan 2019 - Apr 2019 \\
      \hfill \textit{Website: \href{http://ec2-3-212-216-62.compute-1.amazonaws.com/}{http://ec2-3-212-216-62.compute-1.amazonaws.com/}}\\
      % Tools: Python, PyTorch, torchvision, git, scikit-learn, D3.js, Flask, AWS \\
      % \mybullet Trained and tuned CNN classification models using PyTorch and torchvision in Python. \\
      \mybullet Trained and tuned several classification models using sklearn and PyTorch in Python. \\
      \mybullet Obtained best models for each classified using Cohen's Kappa metric. \\
      % \mybullet Created dynamic data visualization to explore models and confusion matrix 
        % using D3.js and Javascript. \\
      \mybullet Created RESTful API service to provide real-time classification and dynamic visualizations
      using Flask-RESTful in Python. \\
      \mybullet Deployed application, models, and visualization to AWS EC2 instance. \\
      % \mybullet Future Work: Implement online learning technique to incorporate feedback from
      % UI to backend model. \\

			\noindent
      \textbf{\href{https://github.com/darkestfloyd/NL2code}{NL2code}} - Natural Language to 
      Python code generator \hfill Jan 2018 - Apr 2018 \\
      \hfill \textit{Project Repository: \href{https://github.com/darkestfloyd/NL2code}{https://github.com/darkestfloyd/NL2code}}\\
      % Tools: Python, TensorFlow, Theano, NLTK, beautifulsoup, git \\
      \mybullet Scraped open-source Python repositories to gather training data 
      using beautifulsoup in Python. \\
      % \mybullet Performed data manipulation using NLTK and Python. \\
      \mybullet Trained custom neural translation system using Theano in Python. \\
      \mybullet Improved accuracy and BLUE score over base paper. \\
      % \mybullet Significant accuracy improvement and minor BLUE score improvement over base paper. \\
      % \mybullet Future Work: Scrape data from leading machine learning repositories in Python for better generalization. \\

			\noindent
      \textbf{\href{https://sichenghao1992.shinyapps.io/DS5110/}{Flashlight}} - Real Estate 
      Property Assessment Visualization for the City of Boston \hfill Oct 2017 - Dec 2017 \\
      \mybullet Created dashboard to visualize various aspects of real estate assessment values 
      using R ``Shiny'' and Leaflet in R. \\
      \mybullet Geocoded missing coordinate values using Open Address dataset and Google Maps Geocode API in Python. \\
      \mybullet Created Python scripts to automate conversion of Zillow's shapefiles to GeoJSON format and gathering of meta-data. \\ 
			
			\noindent
			\textbf{Movie Recommendation System} \hfill Apr 2017 - June 2017\\
			\mybullet Implemented a Recurrent Neural Network using TensorFlow in Python to recommend 
      movies to a user. By analysing \\ \hspace*{9mm} the sequence of movies reviewed, we were 
      able to achieve high scores in peer review. \\ 

% 	% \noindent
% 	% {\large \textbf{PERSONAL PROJECTS}}
% 	% \myline 
% 	% \smallskip
	
% 		% \noindent
% 		% \textbf{Ames Housing Price Prediction} \hfill Oct. - Dec. 2016 \\
%     % \mybullet Created regression models in Scikit-Learn and neural models in TensorFlow to 
%     % predict housing prices in Python. \\
%     % \mybullet Best submission one of top 20\% on Kaggle public leaderboard. \\
		
% 		% \noindent
% 		% \textbf{Melody} - Open-Sourced Music Player Framework for Android \hfill July - Aug. 2015\\
% 		% \mybullet Designed and developed music player framework for Android using RxJava and 
% 			% 		Scala Reactive Extensions, which is freely\\ \hspace*{9mm} available under the MIT 
          % license and is commonly used by Android developers worldwide. \\
	
	\noindent
	{\large \textbf{HONORS AND ACHIEVEMENTS}}
	\myline 
	\smallskip

    \mybullet Panelist for Northeastern University UNCOVER COVID datathon. \hfill Sep 2020 \\
    \mybullet Presented \textit{MURA visualization tool} at The Northeastern University 
    Visualization Consortium. \hfill Apr 2019 \\
    \mybullet Honorable mention for \textit{shinyMRI} by RStudio. \hfill Apr 2019 \\
    \mybullet Graduate speaker for TechTalks at Grad TechDay, Khoury College. \hfill Mar 2019 \\
		\mybullet Coordinated and organized CodeWars, a 24-hour hackathon as part of 
		university fest at Alliance University.\hfill Oct 2015\\
		% \mybullet Volunteer for planting 300 saplings as part of reforestation drive in 
		% Shivaganga Hills, India. \hfill Sept. 2014 \\
		% \mybullet Volunteer for collecting disaster relief supplies for the Uttarakhand Floods 
		% of 2013. \hfill Sept. 2013 \\
		% \mybullet Awarded Karnataka state scholarship, covering 70\% tuition fee for undergraduate 
		% study at Alliance University. \hfill 2013 - 2017 \\


\end{document}
